Databrary: A digital data library for sharing research video

### 2015-01-25 jcdl-15/paper.tex
fill out the rest, good enough for a first draft
some jcdl edits

%%dg tried to add to this section, but it feels like it needs a bit more
Databrary's approach to data is to provide as much context around the primary recordings as possible while still providing contributors some flexibility.
To keep datasets intact, Databrary can incorporate heterogeneous datasets within our target domain by allowing secondary, general-purpose flat-file data, materials, and references to be associated with the primary data.
This facilitates storage and retrieval of data more closely mapped to the original context in which it was collected and analyzed.
At the same time, it provides a common, standard structure for recordings and their associated metadata, including context, contents, and annotations.
We achieve this conformance for previously collected datasets through a combination of in-depth investigative curation and automated, server-side ingest processes.
For datasets that are in the process of being collected, a well-defined user experience provides a platform for researchers to contribute and organize all of their research data as they proceed with their study.
The following section provides specific detail on the design and decision-making behind this unifying structure.

@@

There is also active discussion around the role of repositories and libraries in archiving and providing access to research data \cite{Castelli_etal_2013, Nielson_Hjørland_2014, Macmillan_2014}.
Although this is not directly within our purview, we have laid out a functioning system for research data management that may bring data closer established library standards that achieve these goals.
We may be well positioned to provide interoperability with library-based metadata schemas (Dublin Core, METS) and reach OAI-PMH compliance, so that data researchers add to Databrary can be automatically incorporated into federated library searches with other domain specific data repositories.
By providing a refined API and assigning Digital Object Identifiers (DOIs) to volumes, we can also allow libraries and other information systems to tap into Databrary datasets.

% this is kinda weird, but maybe suitable for a last paragraph?
Our single-minded focus on making collected, identifiable recordings of human research available and reusable to a whole community of researchers gives us a novel perspective on building domain-specific research repositories.
The success we've had in engaging, involving, and extracting data from researchers is due largely to this focus, but it has come at the cost of limitations in scope and difficulties of interoperability and discovery that many more traditional repositories avoid.
By slowly growing our scope and relaxing some of these limitations, we hope to leverage more of the established knowledge of the library science community to start reaping their benefits.

>>>>

Databrary's approach to data is to provide as much context around the primary recordings as possible while still providing contributors some flexibility.
To keep datasets intact, Databrary can incorporate heterogeneous datasets within our target domain by allowing secondary, general-purpose flat-file data, materials, and references to be associated with the primary data.
This facilitates storage and retrieval of data more closely mapped to the original context in which it was collected and analyzed.
At the same time, it provides a common, standard structure for recordings and their associated metadata, including context, contents, and annotations.
We achieve this conformance for previously collected datasets through a combination of in-depth investigative curation and automated, server-side ingest processes.
For datasets that are in the process of being collected, a well-defined user experience provides a platform for researchers to contribute and organize all of their research data as they proceed with their study.
The following section provides specific detail on the design and decision-making behind this unifying structure.

@@

There is also active discussion around the role of repositories and libraries in archiving and providing access to research data \cite{Castelli_etal_2013, Nielson_Hjørland_2014, Macmillan_2014}.
Although this is not directly within our purview, we have laid out a functioning system for research data management that may bring data closer established library standards that achieve these goals.
We may be well positioned to provide interoperability with library-based metadata schemas (such as export of data packages cross-walked to Dublin Core or METS schemas) and reach OAI-PMH compliance, so as to automatically incorporate the data that researchers add to Databrary into federated library searches with other domain specific data repositories.
By providing a refined API and assigning Digital Object Identifiers (DOIs) to volumes, we can also allow libraries and other information systems to tap into Databrary datasets.

% this is kinda weird, but maybe suitable for a last paragraph?
Our single-minded focus on making collected, identifiable recordings of human research available and reusable to a whole community of researchers gives us a novel perspective on building domain-specific research repositories.
The success we've had in engaging, involving, and extracting data from researchers is due largely to this focus, but it has come at the cost of limitations in scope and difficulties of interoperability and discovery that many more traditional repositories avoid.
By slowly growing our scope and relaxing some of these limitations, we hope to leverage more of the established knowledge of the digital library community in order to make this repository more globally applicable to the storage and accessibility of research data.
